---
title: "Untitled"
author: "Vinay Sri Harsha"
date: "8/23/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Reproducible Pitch

- URL: *https://github.com/vmattapalli/Developing-Data-Products*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application."

### Find all details here
URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## mtcars Dataset

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

```{r}
library(randomForest)
library(datasets)
head(mtcars, 3)
```